Reanalysis Step 4: Outcome Analysis with Three-Way Interaction

### 2025-08-20 reanalysis-4-outcome_analysis.qmd
fix

**Treatment Status:**
```{r treatment-dist}
table(imputed_datasets[[1]]$any_treatment) 
```

@@

pooled_results <- data.frame(
  Term = rownames(pooled_summary),
  Estimate = pooled_summary[, "results"],
  SE = pooled_summary[, "se"],
  statistic = pooled_summary[, "(lower"],  
  df = pooled_summary[, "df"],
  p.value = pooled_summary[, "upper)"],
  CI_Lower = pooled_summary[, "2.5 %"],
  CI_Upper = pooled_summary[, "97.5 %"],
  OR = exp(pooled_summary[, "results"]),
  OR_CI_Lower = exp(pooled_summary[, "2.5 %"]),
  OR_CI_Upper = exp(pooled_summary[, "97.5 %"])
)

# Clean column names if needed
names(pooled_results) <- c("Term", "Estimate", "SE", "t_stat", "df", "P_Value", 
                           "CI_Lower", "CI_Upper", "OR", "OR_CI_Lower", "OR_CI_Upper")
# Ensure proper formatting
rownames(pooled_results) <- NULL

@@

```{r pooling-diagnostics}
pool_diag <- data.frame(
  Metric = c("Number of imputations", 
             "Number of parameters",
             "Average degrees of freedom"),
  Value = c(n_imputations,
            nrow(pooled_results),
            round(mean(pooled_results$df), 1))
)

@@

key_terms <- grep("ever_lapse", pooled_results$Term, value = TRUE)[1:min(3, length(grep("ever_lapse", pooled_results$Term, value = TRUE)))]
key_df <- pooled_results[pooled_results$Term %in% key_terms, c("Term", "df")]
key_df$Term <- substr(key_df$Term, 1, 40)
key_df$df <- round(key_df$df, 1)

kable(key_df, caption = "Degrees of freedom for key terms")

>>>>

**Treatment Status:**
```{r treatment-dist}
table(imputed_datasets[[1]]$any_treatment) |> kable()
```

@@

# Check actual structure of pooled_summary
print(names(pooled_summary))
print(colnames(pooled_summary))

# Extract results based on actual MIcombine output structure
# MIcombine typically returns: results, se, (lower, upper), missInfo
pooled_results <- data.frame(
  Term = rownames(pooled_summary),
  Estimate = pooled_summary[, "results"],
  SE = pooled_summary[, "se"],
  CI_Lower = pooled_summary[, "(lower"],  
  CI_Upper = pooled_summary[, "upper)"],
  OR = exp(pooled_summary[, "results"]),
  OR_CI_Lower = exp(pooled_summary[, "(lower"]),
  OR_CI_Upper = exp(pooled_summary[, "upper)"])
)

# Calculate additional statistics if needed
pooled_results$t_stat <- pooled_results$Estimate / pooled_results$SE
pooled_results$P_Value <- 2 * pnorm(-abs(pooled_results$t_stat))
# Ensure proper formatting
rownames(pooled_results) <- NULL

@@

```{r pooling-diagnostics}
# Create diagnostics table
# Note: MIcombine doesn't provide df in the standard output
pool_diag <- data.frame(
  Metric = c("Number of imputations", 
             "Number of parameters"),
  Value = c(n_imputations,
            nrow(pooled_results))
)

@@

# Show key terms with their estimates and CIs
key_terms <- grep("ever_lapse", pooled_results$Term, value = TRUE)[1:min(3, length(grep("ever_lapse", pooled_results$Term, value = TRUE)))]
key_results <- pooled_results[pooled_results$Term %in% key_terms, c("Term", "Estimate", "SE", "P_Value")]
key_results$Term <- substr(key_results$Term, 1, 40)
key_results$Estimate <- round(key_results$Estimate, 3)
key_results$SE <- round(key_results$SE, 3)
key_results$P_Value <- round(key_results$P_Value, 4)

kable(key_results, caption = "Key lapse-related terms")
